\chapter{Conclusions and Future Work}

\section{Summary of Contributions}
\label{sec:conclusions}

This study designed, implemented, and evaluated TechPulse, a cloud-native Hybrid Retrieval-Augmented Generation system for emerging technology intelligence. The key contributions are:

\begin{enumerate}[leftmargin=0.5in]
  \item \textbf{Data Engineering (RQ1):} A deterministic, idempotent ingestion pipeline serves five heterogeneous data sources (ArXiv, Hacker News, DEV.to, GitHub Trending, RSS feeds) with SHA-256 content-addressed deduplication. The pipeline produced a corpus of 3{,}984 documents and 6{,}220 indexed chunks, validated by 208 unit tests across 15 modules.

  \item \textbf{Retrieval Optimization (RQ2):} A five-stage hybrid retrieval pipeline---metadata filtering, vector similarity search, full-corpus BM25, weighted Reciprocal Rank Fusion (vector~0.50, BM25~0.35, recency~0.15), and cross-encoder reranking (ms-marco-MiniLM-L-6-v2)---outperforms the vector-only baseline with a composite quality gain of $+0.047$ (0.723 vs.\ 0.676). Faithfulness improved by $+0.058$, answer relevancy by $+0.065$, and context precision by $+0.070$. Citation grounding remained stable ($-0.020$, no significant difference).

  \item \textbf{Operational Trade-offs (RQ3):} The hybrid pipeline introduces a small latency trade-off (mean 1.13\,s $\to$ 2.49\,s; Cohen's $d = -0.34$, small effect; 95\% CI $[-2.56, -0.72]$\,s). Monthly cost is \$0.33 at 100~queries/day, well within the \$15 budget target and the AWS Free Tier.

  \item \textbf{MLOps Integration (RQ4):} Dual-criteria drift detection (10\% threshold + Shewhart $3\sigma$ with minimum std floor) achieves 100\% accuracy across four simulated drift scenarios. A four-stage CI/CD pipeline (lint, test, build, deploy) using GitHub Actions and AWS SAM ensures reproducible deployments. Eight custom CloudWatch metrics provide operational visibility.
\end{enumerate}

\section{Project Phases}
\label{sec:phases}

The work was organized into four phases, all completed. Table~\ref{tab:remaining_phases} provides a summary.

\begin{table}[H]
\caption{Project Phase Summary.}
\label{tab:remaining_phases}
\centering
\begin{tabular}{p{0.8cm}p{3.5cm}p{2.5cm}p{1.8cm}p{4.0cm}}
\toprule
\textbf{Phase} & \textbf{Focus} & \textbf{Timeline} & \textbf{Status} & \textbf{Key Deliverables} \\
\midrule
A & System Validation \& Corpus Building & Mar W3--W4 & Done & 3{,}984 docs; 6{,}220 chunks; local integration verified \\
B & Evaluation \& Experimentation & Mar W4--Apr W1 & Done & 100-sample eval; statistical analysis (Ch.~5) \\
C & Analysis, Monitoring \& Dashboard & Apr W1--W2 & Done & Drift validation (4/4); visualizations; 9 retrieval improvements \\
D & Final Report \& Submission & Apr W2--W3 & Done & Completed report with empirical evidence \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Phase~A} built the evaluation corpus through sustained multi-cycle ingestion across all five sources (3{,}984 documents, 6{,}220 chunks indexed), verified end-to-end pipeline operation in the local Docker Compose environment, and initiated AWS Free Tier deployment via the SAM template.

\textbf{Phase~B} executed the initial 50-query evaluation in both baseline and hybrid modes, applied Wilcoxon signed-rank tests with Cohen's $d$ and bootstrap 95\% CIs, and profiled per-stage latency with cost projections for 50/100/200 queries/day.

\textbf{Phase~C} applied nine research-backed retrieval improvements (weighted RRF, improved BM25 tokenization, candidate quality gate, asymmetric limits, post-fusion gate, Shewhart std floor, evaluation threading fix, cross-encoder reranking, NaN retry), re-ran the full 100-sample evaluation, validated drift detection (4/4 scenarios correct), and generated result visualizations and comparison tables.

\textbf{Phase~D} completed the evaluation analysis, integrated all empirical findings into the final report, and prepared the submission package.

\section{Known Limitations}
\label{sec:limitations}

\begin{enumerate}[leftmargin=0.5in]
  \item The evaluation corpus is limited to five technology-focused sources; generalizability to other domains requires further study.

  \item The 50-query evaluation set (100 paired observations) provides sufficient power for the paired Wilcoxon test but a larger set would strengthen external validity.

  \item Amazon Bedrock has not been evaluated as the primary backend; however, the evaluation methodology is backend-agnostic, so comparative findings remain transferable.

  \item The \texttt{db.t3.micro} RDS instance may become a bottleneck under high ingestion volumes compared to Aurora Serverless.

  \item The deployed HNSW index (m=16, ef\_construction=64) has not been formally benchmarked against alternative parameter settings or flat-scan baselines; such evaluation is identified as a future direction.

  \item Budget governance via Cost Explorer lags by up to 24 hours; real-time enforcement is not feasible on the Learner Lab.

  \item The test suite (208 tests, 15 modules) covers core logic but lacks end-to-end integration tests with a live database.

  \item The top-$k = 5$ retrieval at 500 tokens/chunk fits Groq and Bedrock context windows but may be silently truncated by Ollama's 4{,}096-token Llama~3.2~3B; a pre-prompt token budget check is identified as a near-term improvement.

  \item API keys are stored as Lambda environment variables; migration to AWS Secrets Manager is recommended for production hardening.
\end{enumerate}

\section{Project Timeline}
\label{sec:timeline}

Figure~\ref{fig:gantt} presents the complete project timeline.

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}

% Header — 9 time columns
\node[font=\small\bfseries] at (-4.0, 0.5) {Phase};
\foreach \m/\lab [count=\i from 0] in {
  1/{Jan},2/{Feb},3/{Mar-W1},4/{Mar-W2},5/{Mar-W3},6/{Mar-W4},7/{Apr-W1},8/{Apr-W2},9/{Apr-W3}} {
  \node[font=\scriptsize\bfseries] at ({\i*1.5+0.75}, 0.5) {\lab};
  \draw[awsgray!20] ({\i*1.5}, -16.2) -- ({\i*1.5}, 0.2);
}

\def\barh{0.40}
\def\rsp{-1.0}  % row spacing

% ================================================================
% COMPLETED ROWS (solid fill)
% ================================================================

% Row 1
\node[font=\scriptsize, anchor=east] at (-0.2, {1*\rsp+0.5}) {Requirements \& Design};
\fill[awsblue!60] (0,{1*\rsp+0.5-\barh/2}) rectangle (3.0,{1*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (1.5, {1*\rsp+0.5}) {\checkmark};

% Row 2
\node[font=\scriptsize, anchor=east] at (-0.2, {2*\rsp+0.5}) {Data Ingestion (5 sources)};
\fill[awsgreen!60] (1.5,{2*\rsp+0.5-\barh/2}) rectangle (6.0,{2*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (3.75, {2*\rsp+0.5}) {\checkmark};

% Row 3
\node[font=\scriptsize, anchor=east] at (-0.2, {3*\rsp+0.5}) {Preprocessing \& Embedding};
\fill[awsgreen!60] (3.0,{3*\rsp+0.5-\barh/2}) rectangle (6.0,{3*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (4.5, {3*\rsp+0.5}) {\checkmark};

% Row 4
\node[font=\scriptsize, anchor=east] at (-0.2, {4*\rsp+0.5}) {Hybrid Retrieval \& RAG};
\fill[awspurple!60] (3.0,{4*\rsp+0.5-\barh/2}) rectangle (7.5,{4*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (5.25, {4*\rsp+0.5}) {\checkmark};

% Row 5
\node[font=\scriptsize, anchor=east] at (-0.2, {5*\rsp+0.5}) {Infrastructure (SAM/CI-CD)};
\fill[awsorange!60] (4.5,{5*\rsp+0.5-\barh/2}) rectangle (7.5,{5*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (6.0, {5*\rsp+0.5}) {\checkmark};

% Row 6
\node[font=\scriptsize, anchor=east] at (-0.2, {6*\rsp+0.5}) {Evaluation Framework (code)};
\fill[awsgreen!60] (4.5,{6*\rsp+0.5-\barh/2}) rectangle (7.5,{6*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (6.0, {6*\rsp+0.5}) {\checkmark};

% ================================================================
% PHASE A — System Validation & Corpus Building (Mar W3 – Mar W4)
% ================================================================
\node[font=\scriptsize\itshape, color=awsgray, anchor=east] at (-0.2, {6.7*\rsp+0.5})
  {\textbf{Phase A}};

% Row 7
\node[font=\scriptsize, anchor=east] at (-0.2, {7*\rsp+0.5}) {Corpus Population};
\fill[awsgreen!60] (6.0,{7*\rsp+0.5-\barh/2}) rectangle (9.0,{7*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (7.5, {7*\rsp+0.5}) {\checkmark};

% Row 8
\node[font=\scriptsize, anchor=east] at (-0.2, {8*\rsp+0.5}) {Docker Integration Testing};
\fill[awsgreen!60] (6.0,{8*\rsp+0.5-\barh/2}) rectangle (7.5,{8*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (6.75, {8*\rsp+0.5}) {\checkmark};

% Row 9  (starts same time as Docker testing, extends to end)
\node[font=\scriptsize, anchor=east] at (-0.2, {9*\rsp+0.5}) {AWS Cloud Deploy (Lab + Free Tier)};
\fill[propblue!25] (6.0,{9*\rsp+0.5-\barh/2}) rectangle (12.0,{9*\rsp+0.5+\barh/2});
\draw[propblue!60, thick] (6.0,{9*\rsp+0.5-\barh/2}) rectangle (12.0,{9*\rsp+0.5+\barh/2});

% ================================================================
% PHASE B — Evaluation & Experimentation (Mar W4 – Apr W1)
% ================================================================
\node[font=\scriptsize\itshape, color=awsgray, anchor=east] at (-0.2, {9.7*\rsp+0.5})
  {\textbf{Phase B}};

% Row 10
\node[font=\scriptsize, anchor=east] at (-0.2, {10*\rsp+0.5}) {Evaluation Run (baseline + hybrid)};
\fill[awsgreen!60] (7.5,{10*\rsp+0.5-\barh/2}) rectangle (10.5,{10*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (9.0, {10*\rsp+0.5}) {\checkmark};

% Row 11
\node[font=\scriptsize, anchor=east] at (-0.2, {11*\rsp+0.5}) {Statistical Analysis \& Latency Profiling};
\fill[awsgreen!60] (9.0,{11*\rsp+0.5-\barh/2}) rectangle (10.5,{11*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (9.75, {11*\rsp+0.5}) {\checkmark};

% ================================================================
% PHASE C — Analysis & Monitoring Validation (Apr W1 – Apr W2)
% ================================================================
\node[font=\scriptsize\itshape, color=awsgray, anchor=east] at (-0.2, {11.7*\rsp+0.5})
  {\textbf{Phase C}};

% Row 12
\node[font=\scriptsize, anchor=east] at (-0.2, {12*\rsp+0.5}) {Drift Validation \& Monitoring};
\fill[awspurple!60] (9.0,{12*\rsp+0.5-\barh/2}) rectangle (10.5,{12*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (9.75, {12*\rsp+0.5}) {\checkmark};

% Row 13
\node[font=\scriptsize, anchor=east] at (-0.2, {13*\rsp+0.5}) {Results Analysis \& Visualization};
\fill[awspurple!60] (9.0,{13*\rsp+0.5-\barh/2}) rectangle (12.0,{13*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (10.5, {13*\rsp+0.5}) {\checkmark};

% Row 14
\node[font=\scriptsize, anchor=east] at (-0.2, {14*\rsp+0.5}) {Dashboard \& Visualization};
\fill[awspurple!60] (9.0,{14*\rsp+0.5-\barh/2}) rectangle (13.5,{14*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (11.25, {14*\rsp+0.5}) {\checkmark};

% ================================================================
% PHASE D — Final Report & Submission (Apr W2 -- Apr W3)
% ================================================================
\node[font=\scriptsize\itshape, color=awsgray, anchor=east] at (-0.2, {14.7*\rsp+0.5})
  {\textbf{Phase D}};

% Row 15
\node[font=\scriptsize, anchor=east] at (-0.2, {15*\rsp+0.5}) {Final Report \& Submission};
\fill[propred!60] (10.5,{15*\rsp+0.5-\barh/2}) rectangle (13.5,{15*\rsp+0.5+\barh/2});
\node[font=\scriptsize, white] at (12.0, {15*\rsp+0.5}) {\checkmark};

% ================================================================
% Completion marker — Apr W3 ≈ x=13.5
% ================================================================
\draw[awsgreen!80!black, very thick, dashed] (13.5, 0.8) -- (13.5, -15.5);
\node[font=\scriptsize\bfseries, awsgreen!80!black] at (13.5, 1.1) {Complete};

% ================================================================
% Legend
% ================================================================
\fill[awsblue!60] (0.5,-18.2) rectangle (1.3,-17.9);
\node[font=\scriptsize, anchor=west] at (1.4, -18.05) {Completed};

\fill[propblue!25] (3.5,-18.2) rectangle (4.3,-17.9);
\draw[propblue!60, thick] (3.5,-18.2) rectangle (4.3,-17.9);
\node[font=\scriptsize, anchor=west] at (4.4, -18.05) {Phase A (Validation)};

\fill[awsorange!20] (7.0,-18.2) rectangle (7.8,-17.9);
\draw[awsorange!60, thick] (7.0,-18.2) rectangle (7.8,-17.9);
\node[font=\scriptsize, anchor=west] at (7.9, -18.05) {Phase B (Evaluation)};

\fill[awspurple!60] (0.5,-18.7) rectangle (1.3,-18.4);
\node[font=\scriptsize, anchor=west] at (1.4, -18.55) {Phase C};

\fill[propred!60] (3.5,-18.7) rectangle (4.3,-18.4);
\node[font=\scriptsize, anchor=west] at (4.4, -18.55) {Phase D (Final Report)};

\end{tikzpicture}%
}
\caption{Project timeline (Gantt chart). All four phases completed.}
\label{fig:gantt}
\end{figure}

\section{Future Extensions}
\label{sec:future}

Several extensions are identified for post-prototype development:

\begin{itemize}[leftmargin=0.5in]
  \item \textbf{Scaling:} Migration to Aurora Serverless; expansion to additional data sources (StackExchange, conference proceedings); ANN-optimized indexing (pgvector HNSW) for sub-linear retrieval at larger corpora
  \item \textbf{Retrieval quality:} Alternative cross-encoder models (e.g., larger ColBERT variants); embedding model fine-tuning or replacement based on drift analysis; adaptive weight tuning for RRF via online feedback
  \item \textbf{Machine learning lifecycle:} Adoption of a formal experiment tracking platform (e.g., MLflow or Weights \& Biases) for versioned evaluation runs; a model registry for embedding and reranker artifacts; domain-specific relevance labeling for supervised fine-tuning of embeddings or rerankers; and periodic re-evaluation triggered by corpus growth milestones
  \item \textbf{Operational hardening:} Full Bedrock evaluation as primary backend; integration test suite with containerized database; token budget management for constrained-context-window backends; Secrets Manager migration for API key handling
  \item \textbf{User experience:} User feedback loop for continuous retrieval quality improvement; query auto-completion; saved searches and alerts for tracked topics
\end{itemize}

\medskip
\noindent This chapter presented the key conclusions and contributions, summarized all four completed project phases, acknowledged known limitations, and outlined future extension directions.
