\chapter{Experimental Plan and Evaluation Metrics}

\section{Evaluation Objective}
\label{sec:eval_objective}

The evaluation operationalises the constrained optimisation objective stated in Equation~\ref{eq:opt} (Chapter~3) and the formal hypotheses H\textsubscript{0}/H\textsubscript{1} (Section~\ref{sec:method_overview}). It aims to answer three questions, each corresponding to a subset of the research questions mapped in Table~\ref{tab:rq_map}: (1) Does hybrid retrieval achieve statistically higher contextual precision and grounding faithfulness than vector-only retrieval (RQ2)? (2) What latency and cost overhead does hybrid retrieval introduce, and does the optimal weight configuration sit within the latency constraint (RQ3)? (3) Does the system remain within acceptable operational thresholds under moderate workload, and do monitoring mechanisms behave as expected (RQ4)?

Statistical significance of mean latency, citation grounding, and context precision differences between baseline and hybrid configurations is assessed using a one-sided Wilcoxon signed-rank test ($\alpha = 0.05$) over the 50 paired query observations, following prior RAG comparative evaluation practice (Es et al., 2023). The statistical analysis is supplemented with Cohen's $d$ effect size and bootstrapped 95\% confidence intervals (1{,}000 resamples) to quantify practical significance beyond $p$-value testing. If H\textsubscript{0} cannot be rejected at the 0.05 level, the evaluation characterises the effect size and identifies corpus or workload conditions under which hybrid retrieval provides practical benefit independent of statistical significance.

\section{Experimental Configurations}
\label{sec:eval_configs}

Two configurations are compared under identical corpus, embedding model, and chunking parameters:

\begin{table}[H]
\caption{Experimental Configuration Comparison.}
\label{tab:exp_configs}
\centering
\begin{tabular}{p{3.5cm}cc}
\toprule
\textbf{Component} & \textbf{Baseline (Vector-Only)} & \textbf{Hybrid (Implemented)} \\
\midrule
Metadata Filtering & $\times$ & \checkmark \\
Vector Similarity & \checkmark & \checkmark \\
Reranking-Lite & $\times$ & \checkmark \\
Recency Weighting & $\times$ & \checkmark \\
Top-$k$ returned & 5 & 5$^{\dagger}$ \\
Embedding Model & MiniLM (384-dim) & MiniLM (384-dim) \\
Cost Governance & None & Budget guard \\
\bottomrule
\end{tabular}
\medskip
\noindent\small{$^{\dagger}$Hybrid retrieval over-retrieves $4 \times k = 20$ candidates at the vector search stage before reranking and final selection of top-5 (see Section~\ref{sec:hybrid}).}
\end{table}

\section{Evaluation Dataset}
\label{sec:eval_dataset}

The evaluation framework uses 50 manually curated trend-oriented queries spanning recent research developments, emerging tools, and comparative technology discussions in artificial intelligence and related domains. Queries are categorized into three types---\textit{research\_trend} (18 queries), \textit{tool\_technology} (16 queries), and \textit{comparative} (16 queries)---and include ground-truth reference answers for automated scoring.

Example queries include: ``What are recent approaches to efficient transformer architectures?''; ``What emerging AI tools are currently being discussed by developers?''; ``How does RAG compare to fine-tuning for domain-specific applications?''; and ``What are recent trends in large language model compression?''

\textbf{Justification for evaluation set size.} The evaluation objective is a controlled comparison between two retrieval configurations under identical corpus and embedding conditions. A paired comparison across 50 carefully constructed queries with ground-truth annotations provides sufficient statistical power to detect meaningful latency, citation grounding, and context precision differences with the Wilcoxon signed-rank test, and exceeds the evaluation scale adopted in prior RAG evaluation work (Es et al., 2023; Saad-Falcon et al., 2023). Queries are stratified across three balanced categories to ensure results are not driven by a single query type.

\section{Evaluation Metrics}
\label{sec:eval_metrics}

Figure~\ref{fig:eval_framework} summarizes the implemented evaluation framework.

% ---- TikZ: Evaluation framework diagram ----
\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}

% Metric boxes (top row)
\node[evalbox=awsblue] (prec) at (-6.0,0)
  {\textbf{Context Precision}\\[2pt]\scriptsize Target: $> 0.75$\\RQ2};

\node[evalbox=awsgreen] (faith) at (-2.0,0)
  {\textbf{Faithfulness}\\[2pt]\scriptsize Target: $\geq 0.80$\\RQ2};

\node[evalbox=awsorange] (lat) at (2.0,0)
  {\textbf{p95 Latency}\\[2pt]\scriptsize Target: $< 2.0$s (retrieval)\\RQ3};

\node[evalbox=awspurple] (cost) at (6.0,0)
  {\textbf{Cost / Month}\\[2pt]\scriptsize Target: $<$ USD~15\\at 1,500 queries/mo\\RQ3};

% Measurement method boxes (bottom row — sources of the metric)
\node[rectangle, draw=awsgray!40, fill=sectionbg, rounded corners=3pt,
      font=\scriptsize, minimum height=0.65cm, text width=3.2cm, text centered]
  (m1) at (-6.0,-1.9) {Measurement:\\RAGAS ContextPrecision\\(Groq judge)};

\node[rectangle, draw=awsgray!40, fill=sectionbg, rounded corners=3pt,
      font=\scriptsize, minimum height=0.65cm, text width=3.2cm, text centered]
  (m2) at (-2.0,-1.9) {Measurement:\\RAGAS Faithfulness\\+ citation ratio};

\node[rectangle, draw=awsgray!40, fill=sectionbg, rounded corners=3pt,
      font=\scriptsize, minimum height=0.65cm, text width=3.2cm, text centered]
  (m3) at (2.0,-1.9) {Measurement:\\Per-query timing\\+ CloudWatch Logs};

\node[rectangle, draw=awsgray!40, fill=sectionbg, rounded corners=3pt,
      font=\scriptsize, minimum height=0.65cm, text width=3.2cm, text centered]
  (m4) at (6.0,-1.9) {Measurement:\\Token count\\$\times$ per-token pricing};

% Arrows point UP: measurement method produces the metric
\draw[parrow] (m1) -- (prec);
\draw[parrow] (m2) -- (faith);
\draw[parrow] (m3) -- (lat);
\draw[parrow] (m4) -- (cost);

% Statistical test annotation — spans all four metric columns
\node[rectangle, draw=propblue!60, fill=propblue!10, rounded corners=3pt,
      font=\scriptsize, text width=13.5cm, text centered, inner sep=3pt]
  (stat) at (0, -3.5) {Statistical test: Wilcoxon signed-rank (one-sided, $\alpha{=}0.05$) applied to paired latency and citation grounding differences ($N{=}50$) \enspace$|$\enspace Cohen's $d$ effect size \enspace$|$\enspace Bootstrap 95\% CI};
\draw[-{Stealth}, dashed, color=propblue!60] (stat.north -| m3.south) -- (m3.south);
\draw[-{Stealth}, dashed, color=propblue!60] (stat.north -| m2.south) -- (m2.south);

\end{tikzpicture}%
}
\caption{Evaluation framework: four measurement dimensions with target thresholds, mapped to research questions.}
\label{fig:eval_framework}
\end{figure}

\subsection{Context Precision}

Retrieval precision is measured using RAGAS \texttt{ContextPrecisionWithoutReference}, which evaluates whether retrieved documents are relevant to the query using automated LLM-based scoring (with Groq \texttt{llama-3.3-70b-versatile} as the evaluation judge).

\subsection{Faithfulness and Hallucination Verification}

Faithfulness is assessed through two complementary mechanisms: (1) RAGAS faithfulness scoring, which decomposes responses into atomic claims and verifies each against retrieved context (target: $\geq 0.80$); and (2) runtime citation grounding ratio, measuring the fraction of response sentences containing valid \texttt{[Source N]} citations (target: $> 0.80$). Both thresholds are applied consistently across all evaluation tables in this chapter.

\subsection{Latency}

End-to-end latency is measured per query, with aggregate statistics computed: mean, median, p95, maximum, and minimum. Latency is decomposed by retrieval mode and query category. The target threshold is p95 $< 2$ seconds for the retrieval component (excluding LLM generation time, which varies by backend).

\subsection{Cost Per Query}

Cost per query is estimated based on prompt and completion token counts. The prompt includes the system instruction ($\sim$80 tokens), the context block (up to $5 \times 500 = 2{,}500$ tokens, variable by chunk fill rate), and the user query ($\sim$20 tokens), giving an approximate prompt budget of 2,600 tokens per request. The completion target is capped at 300 tokens. Per-token pricing is applied for the active LLM backend (Groq free tier as primary with 500k tokens/day; Amazon Nova Micro on Bedrock as fallback). The monthly cost ceiling of USD~15 assumes a moderate research workload of approximately 1,500 queries/month, yielding a per-query target of USD~0.01.

\subsection{Reranking Weight Optimization}

Grid search is performed over the reranking weight space to identify the optimal configuration:

\begin{itemize}[leftmargin=0.5in]
  \item $\alpha \in \{0.4, 0.5, 0.6, 0.7\}$ (semantic similarity weight)
  \item $\beta = \gamma = (1 - \alpha) / 2$ (equal keyword overlap and recency weights)
  \item Constraint: p95 latency $\leq 2.0$ seconds
  \item Objective: maximize mean context precision
\end{itemize}

The configuration yielding the highest mean precision without violating the latency threshold is selected as the production weight configuration.

\subsection{Sensitivity Analysis}
\label{sec:sensitivity}

To justify reranking weight selection beyond grid search, a one-at-a-time (OAT) sensitivity analysis sweeps each parameter ($\alpha$, $\beta$, $\gamma$) independently through $[0.0, 0.1, 0.2, \ldots, 1.0]$ in 11 steps while redistributing the remaining weight proportionally between the other two parameters. This produces 33 evaluation runs and reveals the marginal influence of each parameter on mean similarity and p95 latency, providing empirical evidence for weight selection rather than relying solely on grid search or intuition.

\subsection{Statistical Tests for Baseline vs.\ Hybrid Comparison}
\label{sec:stat_tests}

The baseline-vs-hybrid comparison employs three complementary statistical analyses:

\begin{enumerate}[leftmargin=0.5in]
  \item \textbf{Wilcoxon signed-rank test} (one-sided, $\alpha = 0.05$ and $\alpha = 0.01$) applied to paired latency and citation grounding differences across the 50 query pairs. This non-parametric test is appropriate for the expected non-normal distribution of latency and retrieval quality data.
  \item \textbf{Cohen's $d$ effect size} computed as $d = \bar{x}_{\text{diff}} / s_{\text{diff}}$, where $\bar{x}_{\text{diff}}$ is the mean paired difference and $s_{\text{diff}}$ is its standard deviation. Effect sizes are classified as negligible ($< 0.2$), small ($\geq 0.2$), medium ($\geq 0.5$), or large ($\geq 0.8$).
  \item \textbf{Bootstrap 95\% confidence interval} (1{,}000 resamples with replacement) of the mean latency difference. The 2.5th and 97.5th percentiles provide a model-free estimate of uncertainty that is robust to outliers.
\end{enumerate}

\subsection{Citation Grounding with Partial Relevance}
\label{sec:partial_relevance}

Citation grounding is computed using a weighted relevance scoring function that distinguishes three categories for each citation:

\begin{itemize}[leftmargin=0.5in]
  \item \textbf{Fully Relevant:} keyword overlap between query tokens and cited chunk tokens $\geq 0.5$
  \item \textbf{Partially Relevant:} $0 < \text{overlap} < 0.5$
  \item \textbf{Invalid:} out-of-bounds citation index (references a non-existent source)
\end{itemize}

\noindent The function returns a decomposed grounding report including \texttt{grounding\_ratio} (fraction of valid citations), \texttt{relevance\_score} (mean overlap), and per-class counts (\texttt{full\_count}, \texttt{partial\_count}, \texttt{invalid\_count}). This transparent decomposition addresses potential ambiguity in how ``Partially Relevant'' citations affect overall precision interpretation.

\subsection{Composite Performance Metric}
\label{sec:composite}

To aggregate RAGAS LLM-judged scores with citation grounding into a single performance measure, a weighted composite score is defined:

\begin{equation}
  \text{Composite} = 0.35 \times F + 0.25 \times R + 0.20 \times P + 0.20 \times C
  \label{eq:composite}
\end{equation}

\noindent where $F$ = Faithfulness, $R$ = AnswerRelevancy, $P$ = ContextPrecision, and $C$ = CitationGrounding.

\noindent The weight allocation reflects the primacy of factual correctness (faithfulness, 0.35), followed by answer quality (relevancy, 0.25), and equal contributions from retrieval performance (precision, 0.20) and the system's citation value-add (grounding, 0.20). This composite metric enables direct comparison between baseline and hybrid configurations on a single interpretable scale.

\subsection{Drift Detector Validation}
\label{sec:drift_validation}

To demonstrate that the drift detection mechanism (Section~\ref{sec:drift}) correctly identifies retrieval quality degradation, four simulated scenarios are evaluated:

\begin{enumerate}[leftmargin=0.5in]
  \item \textbf{Healthy baseline} --- establishes baseline from probe query results; verifies no false alarm
  \item \textbf{18\% quality degradation} --- simulated via $0.82\times$ scaling of baseline similarities; verifies threshold detection triggers an alert
  \item \textbf{4\% normal fluctuation} --- simulated via $0.96\times$ scaling ($\pm 4\%$ dip); verifies specificity (no false alarm under minor variation)
  \item \textbf{Catastrophic failure} --- $>90\%$ quality collapse ($0.85 \to 0.05$); verifies both threshold and Shewhart detection mechanisms fire
\end{enumerate}

\noindent Scenarios 1 and 3 validate specificity (no false alarms), while scenarios 2 and 4 validate sensitivity (true positives under degradation).

\textbf{Drift-to-quality impact assessment.} To demonstrate that drift detection improves retrieval quality rather than merely generating operational alarms, the evaluation includes a before/after remediation comparison. When a drift alert fires during the evaluation phase, context precision and faithfulness are measured on the probe query set immediately before remediation (corpus audit and metadata filter re-calibration) and again after remediation is applied. The paired difference in mean context precision quantifies the retrieval quality gain attributable to drift-triggered intervention. Additionally, a counterfactual analysis compares precision trajectories with and without drift-triggered remediation across successive ingestion cycles: the drift-enabled configuration applies corrective action upon alert, while the drift-disabled baseline continues ingesting without intervention. A statistically significant precision divergence (Wilcoxon, $\alpha = 0.05$) between the two trajectories would provide evidence that the drift mechanism contributes to sustained retrieval quality, not just operational visibility.

\subsection{Monthly Cost Projection}
\label{sec:cost_projection}

Cost feasibility is validated by measuring per-query token consumption (prompt + completion) during the evaluation phase and projecting monthly costs for three workload scenarios: 50, 100, and 200 queries/day. The projection includes LLM inference costs (Groq free tier: 500{,}000 tokens/day; Bedrock: pay-per-token) and AWS infrastructure (RDS db.t3.micro, Lambda, S3, SQS within free-tier ceilings). A feasibility assessment flags whether any scenario exceeds the USD~15/month budget target.

\begin{table}[H]
\caption{Summary of Evaluation Metrics and Targets.}
\label{tab:eval_targets}
\centering
\begin{tabular}{p{3.0cm}p{3.0cm}p{3.2cm}p{3.0cm}}
\toprule
\textbf{Metric} & \textbf{Dimension} & \textbf{Method} & \textbf{Target} \\
\midrule
Context Precision & Retrieval quality & RAGAS ContextPrecision (Groq judge) & $> 0.75$ \\
Faithfulness & Grounding quality & RAGAS Faithfulness score & $\geq 0.80$ \\
Citation Grounding Ratio & Hallucination proxy & Weighted partial-relevance analysis & $> 0.80$ \\
Composite Score & Overall quality & $0.35F + 0.25R + 0.20P + 0.20C$ & --- \\
p95 Latency & System performance & Per-query timing (retrieval stage) & $< 2.0$ seconds \\
Cost per Month & Operational cost & Token usage $\times$ per-token pricing & $<$~USD 15 at 1,500 q/mo \\
Wilcoxon $p$-value & Statistical significance & Paired signed-rank test & $< 0.05$ \\
Cohen's $d$ & Effect size & Paired differences & $\geq 0.5$ (medium) \\
Bootstrap 95\% CI & Uncertainty & 1{,}000 resamples & Does not span zero \\
\bottomrule
\end{tabular}
\end{table}

\section{Analysis and Discussion Framework}
\label{sec:discussion}

The following analyses will be conducted upon completion of the Phase~B evaluation run. Targets listed in Table~\ref{tab:eval_targets} are design-time thresholds derived from system requirements and prior RAG benchmarks; empirical validation is pending and will be reported in the final submission.

\textbf{Precision vs.\ computational overhead.} Context precision scores will be compared between baseline and hybrid configurations using paired differences across the 50 evaluation queries. The mean precision improvement will be reported alongside the additional per-query latency introduced by the metadata filtering and reranking stages.

\textbf{Retrieval strictness vs.\ recall.} The 180-day metadata filter and minimum similarity threshold (0.15) reduce retrieval noise but may exclude relevant older documents. The analysis will examine whether filtered-out documents would have contributed positively to generation quality by inspecting borderline cases.

\textbf{Cost--performance balance across LLM backends.} Token usage and estimated cost per query will be reported across backends: Groq (primary, free tier), Ollama (local), and Amazon Bedrock (Free Tier). Since the prompt template is identical across backends, any faithfulness differences can be attributed to model capability rather than retrieval quality.

\textbf{Reranking weight sensitivity.} Grid search results across $\alpha \in \{0.4, 0.5, 0.6, 0.7\}$ will be presented as a precision--latency Pareto frontier to identify the optimal weight configuration. Additionally, a one-at-a-time sensitivity analysis sweeps each parameter ($\alpha$, $\beta$, $\gamma$) through $[0.0, 1.0]$ in 0.1 increments (33 runs total) to quantify marginal parameter influence and provide rigorous justification for weight selection beyond grid search.

\textbf{Production suitability.} The analysis will assess whether all four evaluation targets (context precision $> 0.75$, high faithfulness, p95 latency $< 2$s, cost $<$ USD~15/month) are simultaneously achievable under Free Tier constraints.

\section{Planned Result Visualizations}
\label{sec:visualizations}

This section presents the visualization formats for presenting evaluation results. Placeholder charts illustrate the intended structure; actual data will be populated upon completion of the Phase~B evaluation run and reported in the final submission.

\subsection{Baseline vs.\ Hybrid Retrieval Comparison}

Figure~\ref{fig:viz_comparison} will present a grouped bar chart comparing baseline and hybrid retrieval across four core evaluation metrics: context precision, faithfulness, citation grounding ratio, and normalized latency. This visualization provides the primary evidence for answering Research Question~2 (Section~\ref{sec:rq}).

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=0.92\textwidth,
    height=6.5cm,
    bar width=14pt,
    ylabel={Score},
    ylabel style={font=\small},
    xlabel style={font=\small},
    symbolic x coords={Context Precision, Faithfulness, Citation Grounding, Norm.\ Latency},
    xtick=data,
    xticklabel style={font=\scriptsize, rotate=15, anchor=east},
    yticklabel style={font=\scriptsize},
    ymin=0, ymax=1.05,
    legend style={at={(0.5,1.05)}, anchor=south, legend columns=2, font=\small},
    nodes near coords,
    nodes near coords style={font=\tiny, color=black},
    every node near coord/.append style={yshift=2pt},
    grid=major,
    grid style={gray!20},
    area legend,
]
\addplot[fill=awsblue!60, draw=awsblue] coordinates {
    (Context Precision, 0.00)
    (Faithfulness, 0.00)
    (Citation Grounding, 0.00)
    (Norm.\ Latency, 0.00)
};
\addplot[fill=awsorange!60, draw=awsorange] coordinates {
    (Context Precision, 0.00)
    (Faithfulness, 0.00)
    (Citation Grounding, 0.00)
    (Norm.\ Latency, 0.00)
};
\legend{Baseline (Vector-Only), Hybrid (Implemented)}
\end{axis}

\node[font=\small\itshape, color=propgray, anchor=center] at (6.2, 2.5)
  {Data pending --- evaluation run};
\end{tikzpicture}
\caption{Baseline vs.\ hybrid retrieval comparison across four evaluation dimensions (placeholder --- data pending).}
\label{fig:viz_comparison}
\end{figure}

\subsection{Grid Search: Precision--Latency Pareto Frontier}

Figure~\ref{fig:viz_pareto} will present the grid search results as a scatter plot with the reranking similarity weight ($\alpha$) on the x-axis, context precision on the left y-axis, and p95 latency on the right y-axis. The latency constraint ($\leq 2.0$s) is shown as a horizontal threshold line, enabling identification of the optimal weight configuration that maximizes precision without violating the latency bound.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=0.88\textwidth,
    height=6.5cm,
    xlabel={Similarity Weight ($\alpha$)},
    ylabel={Mean Context Precision},
    xlabel style={font=\small},
    ylabel style={font=\small, color=awsblue},
    xmin=0.35, xmax=0.75,
    ymin=0.0, ymax=1.0,
    xtick={0.4, 0.5, 0.6, 0.7},
    xticklabel style={font=\scriptsize},
    yticklabel style={font=\scriptsize, color=awsblue},
    axis y line*=left,
    grid=major,
    grid style={gray!20},
    legend style={at={(0.02,0.98)}, anchor=north west, font=\small},
]
\addplot[color=awsblue, mark=square*, mark size=3pt, line width=1.2pt]
    coordinates {(0.4, 0.0) (0.5, 0.0) (0.6, 0.0) (0.7, 0.0)};
\addlegendentry{Context Precision}
\end{axis}

\begin{axis}[
    width=0.88\textwidth,
    height=6.5cm,
    ylabel={p95 Latency (seconds)},
    ylabel style={font=\small, color=awsorange},
    xmin=0.35, xmax=0.75,
    ymin=0.0, ymax=3.0,
    xtick=\empty,
    yticklabel style={font=\scriptsize, color=awsorange},
    axis y line*=right,
    axis x line=none,
    legend style={at={(0.98,0.98)}, anchor=north east, font=\small},
]
\addplot[color=awsorange, mark=triangle*, mark size=3pt, line width=1.2pt, dashed]
    coordinates {(0.4, 0.0) (0.5, 0.0) (0.6, 0.0) (0.7, 0.0)};
\addlegendentry{p95 Latency}
\draw[propred, thick, dashed] (axis cs:0.35, 2.0) -- (axis cs:0.75, 2.0)
    node[pos=0.85, above, font=\scriptsize, color=propred] {Latency Target ($\leq 2.0$s)};
\end{axis}

\node[font=\small\itshape, color=propgray, anchor=center] at (6.0, 2.8)
  {Data pending --- grid search};
\end{tikzpicture}
\caption{Grid search: reranking weight ($\alpha$) vs.\ precision and p95 latency (placeholder --- data pending).}
\label{fig:viz_pareto}
\end{figure}

\subsection{Per-Source Retrieval Distribution}

Figure~\ref{fig:viz_sources} will present a stacked bar chart showing the distribution of retrieved documents by source across baseline and hybrid retrieval modes. This visualization reveals whether hybrid retrieval promotes greater source diversity---a key expected benefit of metadata-aware retrieval.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar stacked,
    width=0.7\textwidth,
    height=6.5cm,
    bar width=30pt,
    ylabel={Proportion of Retrieved Documents},
    ylabel style={font=\small},
    symbolic x coords={Baseline, Hybrid},
    xtick=data,
    xticklabel style={font=\small},
    yticklabel style={font=\scriptsize},
    ymin=0, ymax=1.05,
    legend style={at={(1.02,0.5)}, anchor=west, font=\scriptsize, legend columns=1},
    grid=major,
    grid style={gray!20},
    area legend,
]
\addplot[fill=awsblue!70, draw=awsblue] coordinates {(Baseline, 0.20) (Hybrid, 0.20)};
\addplot[fill=awsgreen!60, draw=awsgreen] coordinates {(Baseline, 0.20) (Hybrid, 0.20)};
\addplot[fill=awsorange!60, draw=awsorange] coordinates {(Baseline, 0.20) (Hybrid, 0.20)};
\addplot[fill=awspurple!60, draw=awspurple] coordinates {(Baseline, 0.20) (Hybrid, 0.20)};
\addplot[fill=propgray!50, draw=propgray] coordinates {(Baseline, 0.20) (Hybrid, 0.20)};
\legend{ArXiv, Hacker News, DEV.to, GitHub, RSS}
\end{axis}

\node[font=\small\itshape, color=propgray, anchor=center] at (4.0, 2.8)
  {Uniform placeholder --- actual distribution pending};
\end{tikzpicture}
\caption{Per-source retrieval distribution for baseline vs.\ hybrid modes (placeholder --- data pending).}
\label{fig:viz_sources}
\end{figure}

\subsection{Latency Breakdown by Pipeline Stage}

Figure~\ref{fig:viz_latency} will present a horizontal stacked bar chart decomposing end-to-end latency into four pipeline stages: metadata filtering, vector search, reranking, and LLM generation. This enables identification of the primary latency bottleneck and validates the ``lightweight'' characterization of the reranking stage.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    xbar stacked,
    width=0.85\textwidth,
    height=5.0cm,
    bar width=22pt,
    xlabel={Mean Latency (seconds)},
    xlabel style={font=\small},
    ytick={0,1},
    yticklabels={Baseline,Hybrid},
    yticklabel style={font=\small},
    xticklabel style={font=\scriptsize},
    xmin=0, xmax=3.0,
    ymin=-0.6, ymax=1.6,
    legend style={at={(0.5,-0.3)}, anchor=north, legend columns=4, font=\scriptsize},
    grid=major,
    grid style={gray!20},
    area legend,
]
\addplot[fill=propblue!50, draw=propblue] coordinates {(0.0,0) (0.0,1)};
\addplot[fill=awsblue!50, draw=awsblue] coordinates {(0.0,0) (0.0,1)};
\addplot[fill=awspurple!50, draw=awspurple] coordinates {(0.0,0) (0.0,1)};
\addplot[fill=awsorange!50, draw=awsorange] coordinates {(0.0,0) (0.0,1)};
\legend{Metadata Filter, Vector Search, Reranking, LLM Generation}

\draw[propred, thick, dashed] (axis cs:2.0,-0.6) -- (axis cs:2.0,1.6)
    node[pos=0.85, right, font=\scriptsize, color=propred, xshift=2pt] {p95 Target};
\end{axis}

\node[font=\small\itshape, color=propgray, anchor=center] at (5.5, 2.0)
  {Data pending --- latency profiling};
\end{tikzpicture}
\caption{Latency decomposition by pipeline stage for baseline and hybrid retrieval (placeholder --- data pending).}
\label{fig:viz_latency}
\end{figure}

\subsection{Evaluation Summary Dashboard}

Table~\ref{tab:viz_dashboard} will serve as the primary summary dashboard, consolidating all evaluation metrics into a single comparison table with target thresholds and pass/fail status indicators.

\begin{table}[H]
\caption{Planned Evaluation Summary Dashboard: Baseline vs.\ Hybrid with Target Thresholds.}
\label{tab:viz_dashboard}
\centering
\begin{tabular}{p{3.5cm}p{2.0cm}p{2.0cm}p{2.0cm}p{2.5cm}}
\toprule
\textbf{Metric} & \textbf{Target} & \textbf{Baseline} & \textbf{Hybrid} & \textbf{Status} \\
\midrule
Context Precision & $> 0.75$ & --- & --- & \textit{pending} \\
Faithfulness (RAGAS) & $\geq 0.80$ & --- & --- & \textit{pending} \\
Citation Grounding Ratio & $> 0.80$ & --- & --- & \textit{pending} \\
Composite Score & --- & --- & --- & \textit{pending} \\
p95 Latency (retrieval) & $< 2.0$s & --- & --- & \textit{pending} \\
Mean Latency (retrieval) & --- & --- & --- & \textit{pending} \\
Cost / Month & $<$ USD 15 & --- & --- & \textit{pending} \\
Optimal $\alpha$ & --- & N/A & --- & \textit{pending} \\
Sensitivity Range & --- & N/A & --- & \textit{pending} \\
Wilcoxon $p$-value & $< 0.05$ & N/A & --- & \textit{pending} \\
Cohen's $d$ & $\geq 0.5$ & N/A & --- & \textit{pending} \\
Bootstrap 95\% CI & excl.\ zero & N/A & --- & \textit{pending} \\
Drift Detection Accuracy & 100\% & N/A & --- & \textit{pending} \\
\bottomrule
\end{tabular}
\end{table}

\medskip
\noindent This chapter defined the nine-phase evaluation framework with explicit quantitative targets (context precision~$>$~0.75, faithfulness~$\geq$~0.80, p95 latency~$<$~2.0~s, monthly cost~$<$~USD~15). Results will be populated during the evaluation phase. Chapter~6 documents implementation status and engineering decisions.
