% ============================================================
% TITLE PAGE
% ============================================================
\begin{titlepage}
\begin{center}
\vspace*{0.5cm}
{\fontsize{14}{18}\bfseries\MakeUppercase{%
TechPulse: A Real-Time Hybrid Retrieval-Augmented Generation\\
System for Emerging Technology Intelligence}\\[4pt]
\normalsize\mdseries\textit{Final Report
}}

\vspace{0.6cm}
{\normalsize by}

    \vspace{1em}
    \begin{tabular}{cc}
        Aye Khin Khin Hpone  & Dechathon Niamsa-Ard \\
        {\small (Yolanda Lim) st125970} & {\small st126235}
    \end{tabular}

\vfill

{\normalsize AT82.9002 Selected Topic: Data Engineering and MLOps}\\[6pt]
{\normalsize Instructor: Dr.\ Chantri Polprasert}\\[4pt]
{\normalsize Teaching Assistants: Swaraj Bhanja, Suryansh Srivastava}

\vfill
{\normalsize
Asian Institute of Technology\\[4pt]
School of Engineering and Technology\\[4pt]
Thailand\\[8pt]
April 2026
}
\end{center}
\end{titlepage}

% ============================================================
% ACKNOWLEDGMENTS
% ============================================================
\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}

We express sincere gratitude to Dr.\ Chantri Polprasert, the course instructor, for providing guidance on the system design and evaluation methodology throughout this project. We also thank the teaching assistants, Mr.\ Swaraj Bhanja and Mr.\ Suryansh Srivastava, for their constructive feedback during development milestones.



% ============================================================
% ABSTRACT
% ============================================================
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{ABSTRACT}

Large language models produce hallucinated or outdated outputs when queried about recent developments. Retrieval-Augmented Generation (RAG) mitigates this by grounding generation in retrieved evidence. While hybrid retrieval has been widely studied, its quantitative benefits under cost-constrained, production-oriented settings with single-domain corpora remain insufficiently evaluated.

This study presents TechPulse, a cloud-native Hybrid RAG system for emerging technology intelligence. The system ingests data from five sources (ArXiv, Hacker News, DEV.to, GitHub Trending, RSS feeds) with deterministic preprocessing and MiniLM embedding, indexed in PostgreSQL with pgvector. A five-stage hybrid retrieval pipeline combines metadata filtering, vector similarity search, full-corpus BM25 keyword search, weighted Reciprocal Rank Fusion (RRF; vector~0.50, BM25~0.35, recency~0.15), and cross-encoder reranking (ms-marco-MiniLM-L-6-v2). An automatic LLM fallback chain, dual-criteria drift detection, and three-layer hallucination verification ensure availability and trustworthiness. A 100-sample paired evaluation (50~baseline, 50~hybrid) with RAGAS metrics, Wilcoxon signed-rank testing, and Cohen's~$d$ effect size shows that hybrid retrieval outperforms baseline with a composite quality gain of $+0.047$ (0.723 vs.\ 0.676), driven by faithfulness $+0.058$, answer relevancy $+0.065$, and context precision $+0.070$, at the cost of a moderate latency increase (mean 1.13\,s~$\to$~2.49\,s; Cohen's $d = -0.34$, small effect). Drift detection achieves 100\% accuracy under four simulated drift scenarios. Monthly cost is \$0.33 at 100~queries/day, well within the AWS Free Tier. The results demonstrate that weighted RRF with cross-encoder reranking measurably improves retrieval quality for a single-domain corpus while preserving architectural extensibility for heterogeneous workloads.

\medskip
\noindent\textbf{Keywords:} Retrieval-Augmented Generation; Hybrid Information Retrieval; Vector Databases; Cloud-Native Architecture; MLOps; Semantic Embedding; Emerging Technology Intelligence.

% ============================================================
% FRONT MATTER
% ============================================================
\newpage\tableofcontents

\newpage
\pagenumbering{arabic}


