\chapter*{References}
\addcontentsline{toc}{chapter}{REFERENCES}

{\raggedright
\setlength{\parskip}{8pt}
\everypar{\hangindent=0.5in}

AWS. (2023). \textit{AWS well-architected framework}. Amazon Web Services. \url{https://aws.amazon.com/architecture/well-architected/}

Bayram, F., Ahmed, B. S., \& Kassler, A. (2022). From concept drift to model degradation: An overview on performance-aware drift detectors. \textit{Knowledge-Based Systems}, \textit{245}, 108632. \url{https://doi.org/10.1016/j.knosys.2022.108632}

Borgeaud, S., Mensch, A., Hoffmann, J., Cai, T., Rutherford, E., Millican, K., van den Driessche, G., Lespiau, J.-B., Damoc, B., Clark, A., de Las Casas, D., Guy, A., Menick, J., Ring, R., Hennigan, T., Huang, S., Maggiore, L., Jones, C., Cassirer, A., \ldots Sifre, L. (2022). Improving language models by retrieving from trillions of tokens. In \textit{Proceedings of the 39th International Conference on Machine Learning} (Vol. 162, pp. 2206--2240). PMLR.

Breck, E., Cai, S., Nielsen, E., Salib, M., \& Sculley, D. (2017). The ML test score: A rubric for ML production readiness and technical debt reduction. In \textit{Proceedings of the IEEE International Conference on Big Data} (pp. 1123--1132). IEEE.

Cormack, G. V., Clarke, C. L. A., \& Butt, S. (2009). Reciprocal rank fusion outperforms Condorcet and individual rank learning methods. In \textit{Proceedings of the 32nd International ACM SIGIR Conference on Research and Development in Information Retrieval} (pp. 758--759). ACM. \url{https://doi.org/10.1145/1571941.1572114}

deepset. (2023). \textit{Haystack: Open-source LLM framework to build production-ready applications}. deepset GmbH. \url{https://haystack.deepset.ai/}

InfiniFlow. (2024). \textit{RAGFlow: Deep document understanding-based RAG engine}. InfiniFlow, Inc. \url{https://github.com/infiniflow/ragflow}

TrueFoundry. (2024). \textit{Cognita: RAG framework for production-ready applications}. TrueFoundry. \url{https://github.com/truefoundry/cognita}

Es, S., James, J., Anke, L. E., \& Schockaert, S. (2023). RAGAS: Automated evaluation of retrieval augmented generation. \textit{arXiv preprint arXiv:2309.15217}.

Gama, J., \v{Z}liobait\.{e}, I., Bifet, A., Pechenizkiy, M., \& Bouchachia, A. (2014). A survey on concept drift adaptation. \textit{ACM Computing Surveys}, \textit{46}(4), 1--37. \url{https://doi.org/10.1145/2523813}

Gao, Y., Xiong, Y., Gao, X., Jia, K., Pan, J., Bi, Y., Dai, Y., Sun, J., Wang, M., \& Wang, H. (2023). Retrieval-augmented generation for large language models: A survey. \textit{arXiv preprint arXiv:2312.10997}.

Izacard, G., Lewis, P., Lomeli, M., Hosseini, L., Petroni, F., Schick, T., Dwivedi-Yu, J., Joulin, A., Riedel, S., \& Grave, E. (2022). Atlas: Few-shot learning with retrieval augmented language models. \textit{Advances in Neural Information Processing Systems}, \textit{35}, 22251--22265.

Ji, Z., Lee, N., Frieske, R., Yu, T., Su, D., Xu, Y., Ishii, E., Bang, Y. J., Madotto, A., \& Fung, P. (2023). Survey of hallucination in natural language generation. \textit{ACM Computing Surveys}, \textit{55}(12), 1--38. \url{https://doi.org/10.1145/3571730}

Kreuzberger, D., K\"uhl, N., \& Hirschl, S. (2023). Machine learning operations (MLOps): Overview, definition, and architecture. \textit{IEEE Access}, \textit{11}, 31866--31879. \url{https://doi.org/10.1109/ACCESS.2023.3262138}

LangChain. (2023). \textit{LangChain: Build context-aware reasoning applications}. \url{https://www.langchain.com/}

Lewis, P., Perez, E., Piktus, A., Petroni, F., Karpukhin, V., Goyal, N., K{\"u}ttler, H., Lewis, M., Yih, W.-T., Rockt{\"a}schel, T., Riedel, S., \& Kiela, D. (2020). Retrieval-augmented generation for knowledge-intensive NLP tasks. \textit{Advances in Neural Information Processing Systems}, \textit{33}, 9459--9474.

Lin, J. (2021). A proposed conceptual framework for a representational approach to information retrieval. \textit{ACM SIGIR Forum}, \textit{55}(2), 1--22. \url{https://doi.org/10.1145/3527546.3527552}
Liu, J. (2022). \textit{LlamaIndex: A data framework for LLM applications}. \url{https://www.llamaindex.ai/}

Lu, J., Liu, A., Dong, F., Gu, F., Gama, J., \& Zhang, G. (2018). Learning under concept drift: A review. \textit{IEEE Transactions on Knowledge and Data Engineering}, \textit{31}(12), 2346--2363. \url{https://doi.org/10.1109/TKDE.2018.2876857}

Ma, X., Zhang, X., Pradeep, R., \& Lin, J. (2023). Zero-shot listwise document reranking with a large language model. \textit{arXiv preprint arXiv:2305.02156}.

Manakul, P., Liusie, A., \& Gales, M. J. F. (2023). SelfCheckGPT: Zero-resource black-box hallucination detection for generative large language models. In \textit{Proceedings of the 2023 Conference on Empirical Methods in Natural Language Processing} (pp. 9004--9017). Association for Computational Linguistics.

Min, S., Krishna, K., Lyu, X., Lewis, M., Yih, W.-T., Koh, P. W., Iyyer, M., Zettlemoyer, L., \& Hajishirzi, H. (2023). FActScore: Fine-grained atomic evaluation of factual precision in long form text generation. In \textit{Proceedings of the 2023 Conference on Empirical Methods in Natural Language Processing} (pp. 12076--12100). Association for Computational Linguistics.

Montgomery, D. C. (2020). \textit{Introduction to Statistical Quality Control} (8th ed.). Wiley.

Nogueira, R., \& Cho, K. (2019). Passage re-ranking with BERT. \textit{arXiv preprint arXiv:1901.04085}.

Robertson, S. E., \& Walker, S. (1994). Some simple effective approximations to the 2-Poisson model for probabilistic weighted retrieval. In \textit{Proceedings of the 17th Annual International ACM SIGIR Conference on Research and Development in Information Retrieval} (pp. 232--241). ACM. \url{https://doi.org/10.1007/978-1-4471-2099-5_24}

Saad-Falcon, J., Khattab, O., Potts, C., \& Zaharia, M. (2023). ARES: An automated evaluation framework for retrieval-augmented generation systems. \textit{arXiv preprint arXiv:2311.09476}.

Sculley, D., Holt, G., Golovin, D., Davydov, E., Phillips, T., Ebner, D., Chaudhary, V., Young, M., Crespo, J.-F., \& Dennison, D. (2015). Hidden technical debt in machine learning systems. \textit{Advances in Neural Information Processing Systems}, \textit{28}, 2503--2511.

Shao, Y., Jiang, Y., Kanell, T. A., Xu, P., Khattab, O., \& Lam, M. S. (2024). Assisting in writing Wikipedia-like articles from scratch with large language models. In \textit{Proceedings of the 2024 Conference of the North American Chapter of the Association for Computational Linguistics} (pp. 6252--6278). Association for Computational Linguistics.

Shi, F., Chen, X., Misra, K., Scales, N., Dohan, D., Chi, E. H., Sch\"{a}rli, N., \& Zhou, D. (2023). Large language models can be easily distracted by irrelevant context. In \textit{Proceedings of the 40th International Conference on Machine Learning} (pp. 31210--31227). PMLR.

Thakur, N., Reimers, N., Daxenberger, J., \& Gurevych, I. (2021). BEIR: A heterogeneous benchmark for zero-shot evaluation of information retrieval models. In \textit{Proceedings of the 35th Conference on Neural Information Processing Systems---Datasets and Benchmarks Track}.

Wang, W., Wei, F., Dong, L., Bao, H., Yang, N., \& Zhou, M. (2020). MiniLM: Deep self-attention distillation for task-agnostic compression of pre-trained transformers. \textit{Advances in Neural Information Processing Systems}, \textit{33}, 5776--5788.

Weaviate. (2023). \textit{Verba: The golden RAGtriever}. Weaviate BV. \url{https://github.com/weaviate/Verba}

Zhang, Y., Chen, X., Zhang, Y., Hu, X., Liu, Z., \& Tang, J. (2024). A comprehensive survey on retrieval-augmented generation. \textit{ACM Transactions on Information Systems}. Advance online publication. \url{https://doi.org/10.1145/3703155}

Wheeler, D. J., \& Chambers, D. S. (1992). \textit{Understanding Statistical Process Control} (2nd ed.). SPC Press.

}
